Modeling memory and taxis to analyze migrations

### 2021-06-17 text/ms.Rmd
progress ....

Under what conditions is migration stable:

@@

>>>>

@@

All variables contribute to the ability of the organism to find a stable, migratory state that matches the resource dynamics and maximizes foraging efficiency.

- In general, greater values of $\alpha$ (resource following) lead to an improved ability to match the migration,

- Resource peaks with larger spatial extent (high $\sigma_x$) are smaller duration (low $\sigma_t$) are generally better for migration matching, suggesting that broad but short pulses have the strongest impact on the migration memory.

- Larger values of social attraction ($\beta$) generally lead to poorer migration matching except in those cases where the sociality scale $\lambda$ was high.  Thus, for example, at $\lambda = 20$, no simulations at $\beta >= 200$ managed to acquire or maintain a matched migration.  However, at $\lambda = 50$ or $100$, the migration was slightly better matched at high values of $\beta.  (Fig. **X**)

- Higher diffusion rate
